Topics Causal Inference

### 2024-08-18 documents/paper.tex
Add Introduction.

\section{Introduction}

>>>>

\section{Introduction}
Estimating treatment effects has become a standard practice in applied econometris.
Also, increasingly large datasets are utilized to investigate systematic heterogeneity.
While this has the potential to increase our understanding of say the heterogneous effects of public policies,
from a methodological perspective large datasets with many covariates come at the risk of increased researchers discretion.
In this case, machine learning methods to systematically explore heterogeneity can be helpful to ``tie the researchers hands''.
Furthermore, in high-dimensional settings with a potentially large number of irrelevant covariates, regularization built-in to many machine learning methods is required to deliver useful results.
However, one concern is that many machine learning methods, like the very popular causal forests proposed in~\cite{wager2018estimation}, to estimate conditional average tretment effects rely on a low-dimensional structure of the conditional effects.
Another approach proposed in~\cite{chernozhukov2023genml} is to only estimate low-dimensional features of conditional effects but utilizing machine learning methods in a first-step prediction exercise.
The current paper investigates the performance of these two approaches for data generating processes both with low- and high-dimensional conditional treatment effect structures.
